A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Moded last sentence

Making accurate item-item associations across retailers using only publicly
available information is a challenging problem. The ability to accurately
identify these relationships, however, could potentially provide a retailer or
other service provider with valuable business intelligence.

>>>>

Making accurate item-item associations across retailers using only publicly
available information is a challenging problem. The problem is relevent,
however, and the ability to accurately identify these relationships could 
provide a retailer or other service provider with valuable business
intelligence.
